---
title: "ROP Analysis"
author: "Tom Wright"
date: "February 1, 2016"
output: 
  pdf_document: 
    fig_height: 5
    fig_width: 7
---

Analysis of ROP OCT segmantation data.
Segmentation performed using IOWA reference algorithms.
ETDRS region thickness values extracted using rop_analysis.py scripts

```{r, setup, echo=FALSE}
suppressMessages(library(stringr))
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
suppressMessages(library(reshape2))
```


```{r dataImport, echo=FALSE}
data_dir <- '/mnt/AO/OCT ROP'
files <- list.files(path=data_dir,pattern='*.csv')

loadData <- function(file)
{
  data<-read.csv(file=file,
                 header=TRUE,
                 row.names=1,
                 na.strings='--')
  data$ID <- factor(data$ID)
  return(data)
}
data <- loadData(file.path(data_dir,files[1]))
```

#### Summary

Data loaded from `r nrow(data)` eyes from `r length(levels(data$ID))` subjects.

```{r, echo=FALSE}
#some duplicates here, lets work out why
data %>% 
  group_by(ID) %>% 
  summarise(no_rows=length(ID)) %>% 
  arrange(desc(no_rows))
```
### Notes
*2503689* two exam dates, 2013-10-24 and 2015-10-29
*2511982* two exam dates, 2012-09-09 and 2014-09-22
*2539652* two exam dates, 2013-09-11 and 2013-12-13 
*2487958* two OD analysed 6 & 10, need to select best
*2539016* two exam dates, 2014-03-13 and 2013-09-17, only right eye extracted for 2013-09-17


```{r, echo=FALSE, warnings=FALSE}
#match pattern to extract layer
mp <- 'Output_(.){+}(.csv)'

for(file in files){
  # Extract the filename
  layer <- str_match(file,'Output_(.){+}(.csv)')[2]
  
  data <- loadData(file.path(data_dir,file))
  data_long <- melt(data, 
                    id.vars=c("ID","Eye"),
                    variable.name='Position')
  p <- ggplot(data_long,aes(x=Position, y=value)) +
        geom_boxplot(outlier.shape=NA) +
        geom_point(aes(color=ID), position=position_jitter(width=0.2)) +
        theme_bw() +
        ggtitle(layer) + 
        theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
  suppressWarnings(print(p))
}
```